---
title: "Vocabulary"
author: "Anh Le"
date: "08/12/2014"
output: html_document
---

## The basics

```<<-``` Assign to the parent environment

```all.equal``` Attempt to compare and return TRUE. If not equal, report the difference

```identical(x, y)``` Compare x and y, return TRUE / FALSE

```is.finite``` It's like `is.na` for `NaN`

`%%` indicates `x mod y` and `%/%` indicates integer division.
```{r}
5 %% 2
5 %/% 2
```

`floor()` rounds down, `ceiling()` rounds up, `trunc()` rounds toward 0 (thus behave like `floor` for positive number and like `ceiling` for negative number)

`pmax()` and `pmin()` returns the parallel min and max of the given arguments
```{r}
x <- 1:3; y <- 2:4; pmax(x, y)
```

`rle` is Run length encoding, which is basically a frequency table of values (in vector forms)
```{r}
x <- c(1, 1, 3, 4, 4, 4); rle(x)
```

`setequal` performs set equality (so even if element order is not the same it's ok)
```{r}
setequal(c(1,2,3), c(2,3,1))
```

### Making vector
```{r}
rep(c(1, 2), times=3) # Equivalent rep(c(1, 2), 3)
rep(c(1, 2), length.out=5) # Equivalent rep_len(c(1, 2), 5)
rep(c(1, 2), each=3)
```

```{r}
seq(from=2, to=6, by=1)
seq(from=1, to=5, length.out=4)
seq_len(10) # Faster than seq(length.out=10)
seq_along(c(4,5,6)) # Faster than seq(along.with=c(4,5,6))
```

`combn(x, m, FUN = NULL, simplify = TRUE, ...)` Generate all combinations of the elements of x taken m at a time. Can also apply `FUN` on each (m-long) combination.

### List and data frame
`Split` a vector and data frame
```{r}
x <- c(1, 1, 2, 1, 1, 2)
split(x, f=c(T, T, F)) # Take 2 into a group, 3 into another, and keep doing it
df <- data.frame(value=rnorm(5), state=c("DC", "DC", "NC", "NC", "DC"))
split(df, df$state)
```

### Character manipulation
```{r}
x <- "Mixed"
chartr(old="Mxd", new="mXpa", x)
```

### Factor
`reorder(x, X, FUN)` Reorders the level of `x` based on `FUN(X)`. For example, `reorder(team, fan)` reorder the team according to the number of fan (to use in ggplot, for example).

`relevel(x, ref, ...)` The levels of a factor are re-ordered so that the level specified by ref is first and the others are moved down. This is useful for contr.treatment contrasts which take the first level as the reference.

```{r}
x <- factor(sample(letters[1:5], 10, rep=T))
reorder(x, )
```

